COG-ED Manuscript

### 2022-01-11 06_Paper/COG-ED/Manuscript.Rmd
deleted duplicate lines
table simple slopes analysis adapted

---
title             : "When easy is not preferred: An effort discounting paradigm for estimating subjective values of tasks"
shorttitle        : "The CERED paradigm for estimating subjective values"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1,*"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1,*"
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing
      - Visualization
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote: |
  * Shared first authorship
abstract: |
  When individuals set goals, they consider the subjective value (SV) of both the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
  However, the SV of effort is highly individual, and previous quantification approaches have had two crucial limitations: They presumed a unidirectional relationship between objective task load and the SV of effort, and as a consequence, they could only quantify the SVs of tasks with an objective order of task load.
  One of these approaches is the Cognitive Effort Discounting paradigm by Westbrook et al. (2013).
  We aim to replicate their analysis with our adaptation, the Cognitive and Emotion Regulation Effort Discounting (CERED) paradigm.
  We argue that the CERED paradigm allows two crucial things: Quantifying SVs without assuming that the easiest level is preferred, and quantifying SVs for tasks with no objective order of task load.

@@

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  library(huxtable)     # create huxtable
# library(glmmTMB)      # from the glmmTMB package for multi level models
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
  library(ggplot2)      # for plotting, "ggplot2" package

@@

@@

  # here we repeat the multi level model with all analysis pipelines

  sca_results <- data.frame(pipeline = character(), beta = double(), pvalue = double(), predictor = character())

  # loop through the pipelines

@@

    # combine current results and the bigger data frame

    newdata <- data.frame(pipeline = c(names(pipelines_data[i]),names(pipelines_data[i])),
                          beta = c(summary(m1_sca)$coefficients[2,1],summary(m1_sca)$coefficients[3,1]),
                          pvalue = c(summary(m1_sca)$coefficients[2,5],summary(m1_sca)$coefficients[3,5]),
                          predictor = c("Level", "NFC"))
    sca_results <- rbind(sca_results, newdata)

@@

```{r SCA_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}

  # add a row number and sort the data frame by the fixed effects estimate of the predictor 'level'

  sca_results <- cbind(sca_results, num = rep(c(1:(nrow(sca_results)/2)), each = 2))
  sca_results <- sca_results[order(sca_results$predictor, sca_results$beta, decreasing = TRUE), ]
  sca_results[sca_results$predictor == "NFC", ] <- sca_results[match(sca_results$num[sca_results$predictor == "Level"],
                                                                     sca_results$num[sca_results$predictor == "NFC"]),]

  # lock it in place by turning it into a factor

  sca_results$num <- factor(sca_results$num, levels = sca_results$num[sca_results$predictor == "NFC"])

  # create the upper panel first, which will show the estimates of 'level' and 'nfc'

  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta, color = predictor, group = predictor)) +
    geom_point() +
    geom_line() +
    theme_classic() +
    labs(x = NULL, y = "Fixed effects estimate") +
    scale_y_continuous(position = "right") +
    theme(axis.text.x = element_blank())

>>>>

---
title             : "When easy is not preferred: An effort discounting paradigm for estimating subjective values of tasks"
shorttitle        : "The CERED paradigm for estimating subjective values"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1,*"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1,*"
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    orcid         : "0000-0002-6418-6479"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing
      - Visualization
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote: |
  * Shared first authorship
abstract: |
  When individuals set goals, they consider the subjective value (SV) of both the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
  However, the SV of effort is highly individual, and previous quantification approaches have had two crucial limitations: They presumed a unidirectional relationship between objective task load and the SV of effort, and as a consequence, they could only quantify the SVs of tasks with an objective order of task load.
  One of these approaches is the Cognitive Effort Discounting paradigm by Westbrook et al. (2013).
  We aim to replicate their analysis with our adaptation, the Cognitive and Emotion Regulation Effort Discounting (CERED) paradigm.
  We argue that the CERED paradigm allows two crucial things: Quantifying SVs without assuming that the easiest level is preferred, and quantifying SVs for tasks with no objective order of task load.

@@

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  library(huxtable)     # create huxtable
# library(glmmTMB)      # from the glmmTMB package for multi level models
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package

@@

  m1_h2c.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
                    cond.int = T,                       # print conditional intercepts
                    control.fdr = T,                    # adjust false discovery rate
                    confint = T)                        # add confidence intervals

  #create table
  h2c_ss.table <- data.frame("Value of NFC" = c("- 1 SD", "Mean", "+ 1 SD"),
                             round(m1_h2c.ss$slopes[c(2:5)], digits = 2),
                             round(m1_h2c.ss$slopes[7], digits = 3),
                             round(m1_h2c.ss$ints[c(2,3)], digits = 2))
  colnames(h2c_ss.table) <- c("Value of NFC", "Beta", "$SE$", "95% CI - lower", "95% CI - higher", "$p$-value", "Beta", "$SE$" )
  # columns 2:5 belong to "Slopes of NFC"
  # columns 6:7 belong to "Conditional Intercept"

  h2c_ss.table$`$p$-value`  [which(h2c_ss.table$`$p$-value`<.01)] <- 
    paste0(h2c_ss.table$`$p$-value`[which(h2c_ss.table$`$p$-value`<.01)],"*")
  h2c_ss.table$`$p$-value`[which(h2c_ss.table$`$p$-value`<.05)] <- 
    paste0(h2c_ss.table$`$p$-value`[which(h2c_ss.table$`$p$-value`<.05)],"*")
  h2c_ss.table$`$p$-value`[which(h2c_ss.table$`$p$-value`<.001)] <- 
    paste0("<.001***")

  table_2 <-
    kbl(h2c_ss.table,
    caption = "Interaction between NFC and n-back load level.",
    # "Slopes of n-back level for different NFC values."
    booktabs = T,                          # no vertical lines
    escape = F,                            # correctly print special characters)
    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
            escape = F,                    # correctly print special characters
            threeparttable = T)            # line breaks in the footnote

@@

  # Here we repeat the multi level model with all analysis pipelines.

@@

    # intra-class-correlation

    var_m0_sca <- as.data.frame(VarCorr(m0_sca))
    icc_sca <- var_m0_sca$vcov[1] / (var_m0_sca$vcov[1] + var_m0_sca$vcov[2])

@@
